---
title: "Data Visualization Challenge Entries"
author: "Data Cooperative"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   pdf_document:
     latex_engine: xelatex
params: 
  responses: NULL
  eval_year: NULL
  judge_name: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Data Visualization Challenge

```{r judge-id, results = "asis"}
cat("## Entries for ", params$judge_name, " to evaluate\n")
```

Information for each entry appears on the following pages, one entry per page.
In an effort to reduce implicit biases, each entry is indexed by the first two 
letters of the entrant's first and last name. i.e. Jose Smith would be indexed 
by "JoSm". Score the entry using the corresponding column in the Evaluations
Google Sheet.

For some entries, the submission is an interactive visualization; in 
these cases, see the section "Additional information" to links for interactive 
implementations. Since all images have been reduced to fit on a single page, 
some may be best viewed through a web browser; links to each image can be found
in the "Full image" link. In fact some images are simply too large to be 
displayed on a PDF page; please use the link to the image on Google Drive to 
view the entry (use your UArizona NetID credentials (if you have them) if 
prompted for authorization; if you do not have a UA NetID, use the Google 
account where I have been spamming you with these e-mails).

\newpage

```{r print_entries, results = "asis"}
for (i in 1:nrow(params$responses)) {
  entry <- params$responses[i, ]
  index <- paste0(substr(x = entry$`First Name`, start = 1, stop = 2),
                  substr(x = entry$`Last Name`, start = 1, stop = 2))
  cat("# ", index, "\n")
  cat("## Title: ", entry$Title, "\n")
  cat("### Abstract: \n\n", entry$Abstract, "\n\n")

  # Grab location of image; assumes they are all FiLa.*, where * is a graphics
  # file extension
  image_file <- list.files(path = paste0("data/", params$eval_year, "/images"), 
                           pattern = paste0(index, ".*"),
                           full.names = TRUE)
  
  if (length(image_file) > 0) {
    cat("![Entry for ", index, "](", image_file, ")\n\n")
  } else {
    cat("### Note\n\n")
    cat("The image for this entry is too large to insert, is interactive, or ")
    cat("is animated. Please view online with link below; there may also be ")
    cat("additional details in the Additional information section, below.\n\n")
  }

  cat("### Full image on Google:\n", entry$`Attach static file`, "\n\n")
  
  # Only add Additional information section if there is actually stuff there
  if (!is.na(entry$`Link to additional information`)) {
    cat("## Additional information\n", entry$`Link to additional information`, "\n\n")
  }
  
  cat('\\newpage')
}
```
